Restructuring Data for Exascale Scientific Productivity

### 2016-04-08 papers/2016-Supercomputing/paper.tex
skeleton
Add interpolation details. Add self as author.

\documentclass{sig-alt-gov2}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% \usepackage{subfig}
\usepackage{subfigure}
\usepackage[pdftex]{}
\usepackage{graphicx}
% \usepackage{todonotes}
\usepackage{listings}
\usepackage{comment}
\lstset {% general command to set parameter(s)
  language=C,
  basicstyle=\footnotesize,               % print whole listing small
  % keywordstyle=\color{black}\bfseries, % underlined bold black keywords
  % identifierstyle =\color{black},  % nothing happens
  % commentstyle=\color{black}\emph, % white comments
  % stringstyle=\ttfamily,          % typewriter type for strings
  % stringstyle=\color{black},       % typewriter type for strings
  tabsize=4,
  showtabs=false,
  showstringspaces=false}
% can't figure this one out for particles bandwidth
% \usepackage[caption,label]{subfig}

@@

\numberofauthors{1}
\author{
  \alignauthor {
    Jay Lofstead\footnotemark[1]~~,
    Hasan Abbasi\footnotemark[3]~~,
    Mark Ainsworth\footnotemark[6]~\footnotemark[3]~~,
    Jong Choi\footnotemark[3]~~,
    Matthew Curry\footnotemark[1]~~,\\
    Scott Klasky\footnotemark[3]~\footnotemark[4]~\footnotemark[7]~~,
    Tahsin Kurc\footnotemark[9]~~,
    Qing Liu\footnotemark[3]~~,
    Jeremy Logan\footnotemark[4]~~,
    Carlos Maltzahn\footnotemark[2]~~,
    Manish Parashar\footnotemark[5]~~,\\
    Norbert Podhorzski\footnotemark[3]~~,
    Feiyi Wang\footnotemark[3]~~,
    Matthew Wolf\footnotemark[7]~~,
    C. S. Chang\footnotemark[8]~~,
    Michael Churchill\footnotemark[8]~~,
    Stephane Ethier\footnotemark[8]~~
  }\\
  \footnotemark[1]~~Sandia National Laboratories,
  \footnotemark[2]~~University of California Santa Cruz,\\
  \footnotemark[3]~~Oak Ridge National Laboratory,
  \footnotemark[4]~~U. Tenn. Knoxville,
  \footnotemark[5]~~Rutgers University,\\
  \footnotemark[6]~~Brown University,
  \footnotemark[7]~~Georgia Tech,
  \footnotemark[8]~~PPPL,
  \footnotemark[9]~~Stony Brook
}
\maketitle

@@

\section{Motivation and Application Use Cases}
\label{motivation}

\section{Storage Hierarchy}
\label{storage-h}

\section{Partitioning Techniques}
\label{details}

\section{Evaluation Platform}
\label{hardware}

\section{Cost-Benefit Discussion}
\label{discussion}

>>>>

\documentclass{sig-alt-gov2}
\pdfpagewidth=8.5in
\pdfpageheight=11in
% \usepackage{subfig}
\usepackage{subfigure}
\usepackage[pdftex]{}
\usepackage{graphicx}
\usepackage{listings}
\usepackage{comment}

\usepackage{stys/interpolation}
\usepackage{enumerate}

\lstset {% general command to set parameter(s)
  language=C,
  basicstyle=\footnotesize,               % print whole listing small
  % keywordstyle=\color{black}\bfseries, % underlined bold black keywords
  % identifierstyle =\color{black},  % nothing happens
  % commentstyle=\color{black}\emph, % white comments
  % stringstyle=\ttfamily,          % typewriter type for strings
  % stringstyle=\color{black},       % typewriter type for strings
  tabsize=4,
  showtabs=false,
  showstringspaces=false}
% can't figure this one out for particles bandwidth
% \usepackage[caption,label]{subfig}

@@

\numberofauthors{1}
\author{
  \alignauthor {
    Jay Lofstead\footnotemark[1]~~,
    Hasan Abbasi\footnotemark[3]~~,
    Mark Ainsworth\footnotemark[6]~\footnotemark[3]~~,
    Jong Choi\footnotemark[3]~~,
    Matthew Curry\footnotemark[1]~~,\\
    Scott Klasky\footnotemark[3]~\footnotemark[4]~\footnotemark[7]~~,
    Tahsin Kurc\footnotemark[9]~~,
    Qing Liu\footnotemark[3]~~,
    Jeremy Logan\footnotemark[4]~~,
    Carlos Maltzahn\footnotemark[2]~~,
    Manish Parashar\footnotemark[5]~~,\\
    Norbert Podhorzski\footnotemark[3]~~,
    Feiyi Wang\footnotemark[3]~~,
    Matthew Wolf\footnotemark[7]~~,
    Ben Whitney\footnotemark[6]~~,
    C. S. Chang\footnotemark[8]~~,
    Michael Churchill\footnotemark[8]~~,
    Stephane Ethier\footnotemark[8]~~
  }\\
  \footnotemark[1]~~Sandia National Laboratories,
  \footnotemark[2]~~University of California Santa Cruz,\\
  \footnotemark[3]~~Oak Ridge National Laboratory,
  \footnotemark[4]~~U. Tenn. Knoxville,
  \footnotemark[5]~~Rutgers University,\\
  \footnotemark[6]~~Brown University,
  \footnotemark[7]~~Georgia Tech,
  \footnotemark[8]~~PPPL,
  \footnotemark[9]~~Stony Brook
}
\maketitle

@@

\section{Motivation and Application Use Cases}
\label{motivation}
\input{motivation.tex}

\section{Storage Hierarchy}
\label{storage-h}
\input{storage.tex}

\section{Partitioning Techniques}
\label{details}
\input{details.tex}

\section{Evaluation Platform}
\label{hardware}
\input{hardware.tex}

\section{Evaluation}
\label{performance}
\input{performance.tex}

\section{Cost-Benefit Discussion}
\label{discussion}
\input{discussion.tex}
